Allometric growth of invasive lionfish varies by region in the Western Atlantic

### 2018-06-05 docs/Manuscript.Rmd
Mostly minor changes.  One "major" comment in line 184.
Other notes:

Put citations in chronological order (or alphabetical - whatever the journal does. But they need to be in order).

Reduce the number of citations per parentheses (line 50).

---
title: Invasive lionfish present region-wide variation of allometric growth in the Western Atlantic
abstract: "Lionfish (*Pterois volitans / miles*) are an invasive species in the Western Atlantic and the Caribbean. Improving management of invasive lionfish populations requires accurate estimates of total biomass, which depend on accurate estimates of the length-weight relationship. Lionfish exhibit a sedentary behavior that is likely to result in high levels of spatial variation in some life history characterstics, such as the length-weight relationship. We review 12 published length-weight relationships of lionfish taken throughout their invasive range and describe the spatial variation and implications of these differences. The spatial pattern observed here is consistent with those reported in genetic studies or age-at-length studies. We show that the use of *ex situ* parameters can result in up to a three-fold overestimation of Total Weight, but that using parameters obtained nearby reduces this error. These findings can have major implications for management in terms of predicting effects on local ecosystems, evaluating the effectiveness of removal programs, or estimating biomass available for harvest."
output:
  pdf_document:
    keep_tex: yes
    number_sections: no
    template: peerj_template.tex
---

@@

Invasive lionfish are primarily studied in coral reef ecosystems, where their impacts are far-reaching. For example, field experiments by \citet{albins_2008} showed that lionfish establishment led to reduced recruitment of native fishes by nearly 80% over a five week period in Florida. \citet{green_2012} report that prey fish biomass declined 65% over two years as lionfish biomass increased along Bahamian coral reefs. Lionfish have also established invasive populations in other habitats such as estuaries, mangroves, hard-bottomed areas, and mesophotic reefs \citep{jud_2011,barbour_2010,muoz_2011,andradibrown_2017,claydon_2012}.

A substantial amount of research describes lionfish feeding ecology throughout the invaded range \citep{muoz_2011,morris_2009,cote_2013,dahl_2014,valdezmoreno_2012,villaseorderbez_2014,hackerott_2017,sandel_2015}. A meta-analysis by  \citet{peake_2018} showed that invasive lionfish prey on at least 167 different species across the tropical and temperate North Atlantic. Their feeding behavior and high consumption rates can reduce recruitment and population sizes of native reef-fish species, and can further endanger reef fish \citep{albins_2008, green_2012,rocha_2015}. (However, see \citet{hackerott_2017} for a case where there was no evidence that lionfish affected the density, richness, or community composition of prey fishes). Major efforts have been made to understand the possible impacts of the invasion by tracking the spread of established lionfish populations through time \citep{schofield_2009,schofield_2010} and by predicting invasion ranges under future climates \citep{grieve_2016}. It{s been proposed that trophic impacts of lionfish can be minimized if local lionfish biomass is controled by culling \citep{ariasgonzalez_2011}.

Governments and non-profit organizations have sought to reduce lionfish densities through removal programs and incentivizing its consumption \citep{chin_2016}. In some cases, these have shown to significantly reduce --but not quite eliminate-- lionfish abundances at local scales \citep{sandel_2015,chin_2016,deleon_2013}. In addition, culling programs can help stabilize or grow native prey fish populations \citep{cote_2014}. Complete eradication of lionfish through fishing is unlikely because of their rapid recovery rates and ongoing recruitment to shallow-water areas from their persistent populations in mesophotic coral ecosystems \citep{barbour_2011,andradibrown_2017}. However, promoting lionfish consumption might create a level of demand capable of sustaining a stable fishery, which can help control shallow-water populations while providing alternative livelihoods and avoiding further impacts to local reef biota \citep{chin_2016}.

The feasibility of establishing fisheries through lionfish removal programs has been extensively evaluated through field observations and empirical modeling \citep{barbour_2011,morris_2011,deleon_2013,johnston_2015,sandel_2015,chin_2016,usseglio_2017}. One contributing factor to the success of many removal programs is the sedentary nature of adult lionfish \citep{jud_2012}. Culling programs are effective in reducing local adult populations largely because lionfish exhibit high levels of site fidelity and rarely leave their home range \citep{Fishelson_1997,cote_2014,kochzius_2005}. Fish with this sedentary behavior are likely to exhibit high levels of spatial variation in important life history characterstics such as growth or natural mortality rates \citep{hutchinson_2008,wilson_2012}. The importance of considering spatial heterogeneity is well-documented in terms of assessing and managing sedentary species \citep{gunderson_2008,guan_2013}, and such variation should be accounted for when evaluating the feasibility of establishing lionfish fisheries as well.

Determining the feasibility of such initiatives require modeling changes in biomass in response to changes in mortality (*i.e.* culling). A common way to model this is via length-structured population models, where fish lengths are converted to  weight to calculate total biomass \citep{cote_2014,barbour_2011,andradibrown_2017}. The length-weight relationship is therefore an essential component of these models, but this relationship can vary across regions as a response to biotic (*e.g.* local food availability) and abiotic (*e.g.* water temperature) conditions \citep{johnson_2016}. Literature suggests that site-specific parameters are necessary in order to accurately estimate biomass when length-weight relationships are spatially variable, and this variability becomes increasingly important when estimating the potential effectiveness and feasability of lionfish culling programs or when identifying total biomass available for harvest by fishers \citep{barbour_2011,morris_2011,johnston_2015,chin_2016,cote_2014}. In addition to environmentally-driven spatial variation, genetic analysis of invasive lionfish suggest biological differences due to the existence of two genetically distinct subpopulations between the northwest Atlantic and the Caribbean \citep{betancurr_2011}. To date, no studies have examined region-wide differences in length-weight parameters despite the large number of studies reporting this relationship for lionfish.

The objective of this paper is to describe the spatial pattern of length-weight relationships of lionfish in the Caribbean and Western Atlantic and evaluate the implications of these spatial differences. Length-weight relationships for lionfish exist for North Carolina, Northern and Southern Gulf of Mexico, the Southern Mexican Caribbean, Bahamas, Little Cayman, Jamaica, Bonaire, Puerto Rico, and Costa Rica \citep{barbour_2011,fogg_2013,dahl_2014,aguilarperera_2016,sabidoitza_2016,sabidoitz_2016,darling_2011,edwards_2014,chin_2016,deleon_2013,toledohernndez_2014,sandel_2015}. This study also provides the first length-weight relationship for the central Mexican Caribbean.

@@

We reviewed 12 published studies and obtained 17 length-weight relationships for the North Atlantic (n = 1), Gulf of Mexico (n = 7), and Caribbean (n = 10, Table \ref{tab:all_params}, Fig \ref{fig:all_allo}). We collected information on sampling methods, sex differentiation, location, and depth ranges from each study when available, and assumed both genders were included in a study if gender was unspecified. Only two studies reported parameters for each gender \citep{aguilarperera_2016,fogg_2013}. Reviewed studies presented information for organisms obtained at depths between `r min(review$minD, na.rm = T)` m and `r max(review$maxD, na.rm = T)` m. Three studies explicitly stated that their organisms were sampled with pole spears \citep{aguilarperera_2016,chin_2016,dahl_2014,sabidoitz_2016}, and five studies mentioned that some of their organisms were obtained with pole spears (or other type of harpoon) but also hand-held nets or fish traps \citep{sandel_2015,barbour_2011,fogg_2013,edwards_2014,sabidoitza_2016,sabidoitz_2016,toledohernndez_2014}, and two studies did not specify how organisms were sampled \citep{deleon_2013,darling_2011}. \citet{fogg_2013} use spine-less weight in the length-weight relationship estimation, and thus their parameters likely underestimate total wieght. Since no spine-less to total weight conversions were available, these parameters were taken as reported.

@@

Where $a$ is the ponderal index and $b$ is the scaling exponent or allometric parameter. When $b = 3$, it is said that the organism exhibits a perfect isometric growth. Transforming this equation via base-10 logarithms:

@@

Where $Y = log_{10}(TW)$, $X = log_{10}(TL)$, and $c = log_{10}(a)$. The coefficients ($c$ and $b$) were estimated with  an Ordinary Least Squares Regression and heteroskedastic-robust standard error correction \citep{zeileis_2004}. The $b$ coefficient was tested against the null hypothesis of isometric growth (*i.e.* $H_0: b = 3$). Coefficients were tested with a two-tailed Student's t, and the significance of the regression was corroborated with an F-test.

@@

Combining the length-weight parameters extracted from the literature and the additional pair calculated here, we obtain a total of 18 pairs. We use the central Mexican Caribbean as a case study of how the use of *ex situ* parameters influences the accuracy of weight estimates for lionfish. We estimated TW from the TL observations we collected in the central Mexican Caribbean (n = 109) using each of the 18 parameter pairs and divided predicted weights by known observed weights to obtain a simple measure of over- or underestimation. Difference in mean weight ratios across the different parameter pairs were tested with a one-way analysis of variance (ANOVA) and Tuskey's test was used for post-hoc tests. All analyses were performed in R version `r paste(version$major, version$minor, sep = ".")` \citep{rcore_2018}. Raw data and code used in this work are available at dryad.org.

@@

Figure \ref{fig:all_allo} shows the length-weight relationships with parameters from all studies. Parameters from models fit to males or females exclusively tend to have a higher steepness (*i.e.* higher allometric parameter), with mean $\pm$ standard deviation values of $b = `r formatC(mean(review$b[review$Gender == "Male"]), digits = 2, format = "f")` \pm `r formatC(sd(review$b[review$Gender == "Male"]), digits = 2, format = "f")`$ and $b = `r formatC(mean(review$b[review$Gender == "Female"]), digits = 2, format = "f")` \pm `r formatC(sd(review$b[review$Gender == "Female"]), digits = 2, format = "f")`$ for males and females respectively, compared to parameters from models for combined genders with a mean $\pm$ standard deviation value of $b = `r formatC(mean(review$b[review$Gender == "Both"]), digits = 2, format = "f")` \pm `r formatC(sd(review$b[review$Gender == "Both"]), digits = 2, format = "f")`$. In the case of the ponderal index ($a$) and its $log_{10}$ transformation ($c$), values were higher for parameters for combined genders.

There were significant differences in our predicted weights for the central Mexican Caribbean when using the different pairs of parameters ($F(df = 15; 1728) = 38.26; p < 0.001$). Weight estimates using parameters from the Gulf of Mexico and North-Western Atlantic were higher on average than those from the Caribbean. The average ($\pm$ SD) predicted-to-observed weight ratios from these three regions were 1.24 $\pm$ 0.309, 1.76 $\pm$ 0.496, and 1.17 $\pm$ 0.398, respectively. The lowest weight estimates resulted from using the allometric parameters from Banco Chinchorro in the Caribbean \citet{sabidoitz_2016}, and the highest weight estimates came from the Northern Atlantic \citep{barbour_2011}. The calculated ratio of predicted-to-observed weight  ranged from `r filter(Predicted_biomass, Study_id == "Sabido2BC") %$% mean(Biomass_ratio) %>% formatC(digits = 2, format = "f")` $\pm$ `r filter(Predicted_biomass, Study_id == "Sabido2BC") %$% sd(Biomass_ratio) %>% formatC(digits = 2, format = "f")` to `r filter(Predicted_biomass, Study_id == "Barbour") %$% mean(Biomass_ratio) %>% formatC(digits = 2, format = "f")` $\pm$ `r filter(Predicted_biomass, Study_id == "Barbour") %$% sd(Biomass_ratio) %>% formatC(digits = 2, format = "f")` (mean $\pm$ SD). Tukey's post-hoc test suggests that weight ratios for the central Mexican Caribbean were not differnt from those obntained with parameters from Little Cayman, the Bahamas, and some sites in the Gulf of Mexico (Tukeys HSD $p > 0.05$). Predicted-to-observed weight ratios are presented in Figure \ref{fig:bio_ratio}. Spine-less weight parameters from \citet{fogg_2013} still produced predicted-to-observed weight ratios > 1.

@@

We  detected substantial differences in weight-at-length between organisms from the Caribbean and Gulf of Mexico / North-Western Atlantic. The groupings of predicted-to-observed weight ratios were consistent with the spatial distribution of the studies, suggesting that these differences are mediated by space. These length-weight differences mirror similar findings of regional variability in age-at-length relationships of lionfish across both their invaded and native regions \citep{pusack_2016}. These patterns may be driven by genetic variation or by organisms being exposed to distinct environmental conditions. For example, \citet{betancurr_2011} used mitochondrial DNA to demonstrate the existence of two distinct population groups, identified as the “Caribbean group” and “Northern Group”, and \citet{fogg_2015} alternatively suggested that age-at-length differences may be driven by climate. Differences in weight-at-length could also reflect differences in energy input or differential usage of this energy, or a combination of both. Future research is needed to determine which processes are at work here.

Differences in length-weight relationships have traditionally been highlighted as potential pitfalls to fishery management. For example, \citet{wilson_2012} show that small-scale variations in length-at-age and fishing mortality in other Scorpaeniformes translate to differential landings, effort, and catch per unit effort in the live fish fishery of California, and that these differences must be taken into account in management plans. The lionfish case poses the opposite scenario, where the manager desires to erradicate species. To accurately gauge both the effectiveness of lionfish removal efforts and the resources needed to successfully manage an invasion, we must acknowledge and understand regional biological differences in important variables such as allometric growth parameters.

The results presented here have major implications for management. For example, \citet{edwards_2014} simulated a lionfish culling program under two scenarios, one using length-at-age and length-to-weight parameters from North Carolina and one using parameters from Little Cayman. Their results show that using different parameters caused up to a four-year difference in the time required for the simulated lionfish population to recover to 90% of its initial biomass after removals ceased. Here, we show that using one set of length-weight parameters versus another for a given length can result in up to a threefold TW overestimation. These spatially-driven differences become especially important when allocating resources for lionfish removal programs, incentivizing its fishery as a source of alternative livelihoods, or estimating ecosystem impacts. Research efforts focused on invasive lionfish populations need to use parameters calculated for their region to the extent possible, or at least use reasonable sets of different parameters that provide upper and lower bounds in their results.

\section*{Aknowledgements}

>>>>

---
title: Allometric growth of invasive lionfish varies by region in the Western Atlantic
abstract: "Lionfish (*Pterois volitans / miles*) are an invasive species in the Western Atlantic and the Caribbean. Improving management of invasive lionfish populations requires accurate total biomass estimates, which depend on accurate estimates of allometric growth. Sedentary species like lionfish often exhibit high levels of spatial variation in life history characterstics, so we review 12 published length-weight relationships for lionfish taken throughout their invasive range and found substantial regional differences in allometric growth parameters. The spatial pattern we observed is consistent with findings from other studies focusing on genetics or age-at-length. We show that the use of *ex situ* parameters can result in up to a threefold overestimation of total weight, but using parameters from nearby regions reduces this error. These findings can have major implications for management in terms of predicting effects on local ecosystems, evaluating the effectiveness of removal programs, or estimating biomass available for harvest."
output:
  pdf_document:
    keep_tex: yes
    number_sections: no
    template: peerj_template.tex
---

@@

Invasive lionfish are primarily studied in coral reef ecosystems, where their impacts are far-reaching. For example, field experiments by \citet{albins_2008} showed that lionfish establishment led to reduced recruitment of native fishes by nearly 80% over a five week period in Florida. \citet{green_2012} reported that prey fish biomass declined by 65% over two years as lionfish biomass increased along Bahamian coral reefs. Lionfish have also established invasive populations in other habitats such as estuaries, mangroves, hard-bottomed areas, and mesophotic reefs \citep{jud_2011,barbour_2010,muoz_2011,andradibrown_2017,claydon_2012}.

<!-- You need to put references in chronological order -->

A substantial amount of research describes lionfish feeding ecology throughout its invaded range \citep{muoz_2011,morris_2009,cote_2013,dahl_2014,valdezmoreno_2012,villaseorderbez_2014,hackerott_2017,sandel_2015}. A meta-analysis by  \citet{peake_2018} showed that invasive lionfish prey on at least 167 different species across the tropical and temperate North Atlantic. Their feeding behavior and high consumption rates can reduce recruitment and population sizes of native reef-fish species, and can further endanger reef fish \citep{green_2012,rocha_2015}. However, see \citet{hackerott_2017} for a case where there was no evidence that lionfish affected the density, richness, or community composition of prey fishes. Major efforts have been made to understand possible impacts of the lionfish invasion by tracking the spread of established populations through time and by predicting invasion ranges under future climates \citep{schofield_2009,schofield_2010,grieve_2016}. Also, \citet{ariasgonzalez_2011} proposed that trophic impacts of lionfish can be minimized if local lionfish biomass is controlled by culling.

<!-- You cite the same papers over and over. It's good to have them all in there at least once, but you don't need to cite every paper every time.  For example, you cite Chin 2016 6 times in the introduction. You can probably take half of those out.  When you over-list references, it makes it seems like you're overcompensating for a lack of info in your own work or that you're too lazy to figure out which 2-3 references are actually the most relevant to the point you're making -->

Governments and non-profit organizations have sought to reduce lionfish densities through removal programs and incentivizing its consumption \citep{chin_2016}. In some cases, these have shown to significantly reduce --but not quite eliminate-- lionfish abundances at local scales \citep{sandel_2015,chin_2016,deleon_2013}. In addition, culling programs can help stabilize or grow native prey fish populations \citep{cote_2014}. Complete eradication of lionfish through fishing is unlikely because of their rapid recovery rates and ongoing recruitment to shallow-water areas from persistent populations in mesophotic coral ecosystems \citep{barbour_2011,andradibrown_2017}. However, promoting lionfish consumption might create a level of demand capable of sustaining a stable fishery, which can help control shallow-water populations while providing alternative livelihoods and avoiding further impacts to local reef biota \citep{chin_2016}.

The feasibility of establishing fisheries through lionfish removal programs has been extensively evaluated through field observations and empirical modeling \citep{barbour_2011,morris_2011,deleon_2013,johnston_2015,sandel_2015,chin_2016,usseglio_2017}. One factor contributing to the success of many removal programs is the sedentary nature of adult lionfish \citep{jud_2012}. Culling programs are effective in reducing local adult populations largely because lionfish exhibit high levels of site fidelity and rarely leave their home range \citep{Fishelson_1997,cote_2014,kochzius_2005}. Fish with sedentary behavior are likely to exhibit high levels of spatial variation in important life history characterstics such as growth or natural mortality rates, and the importance of considering spatial heterogeneity is well-documented in terms of assessing and managing sedentary species \citep{gunderson_2008,hutchinson_2008,wilson_2012,guan_2013}. Such variation should be accounted for when evaluating the viability of establishing lionfish fisheries as well.

Determining the feasibility of such initiatives requires modeling the change in biomass in response to changes in mortality (*i.e.* culling). A common way to model this is via length-structured population models, where fish lengths are converted to  weight to calculate total biomass \citep{cote_2014,barbour_2011,andradibrown_2017}. The allometric length-weight relationship is therefore an essential component of these models, but this relationship can vary across regions as a response to biotic (*e.g.* local food availability) and abiotic (*e.g.* water temperature) conditions \citep{johnson_2016}. Literature suggests that site-specific parameters are necessary in order to accurately estimate biomass when allometric relationships are spatially variable, and this variability is increasingly important when estimating the potential effectiveness of lionfish culling programs or when identifying total biomass available for harvest by fishers \citep{barbour_2011,morris_2011,johnston_2015,chin_2016,cote_2014}. Genetic analysis of lionfish suggests biological differences due to the existence of two genetically distinct invasive subpopulations between the northwest Atlantic and the Caribbean \citep{betancurr_2011}. However, no studies have examined region-wide differences in allometric growth parameters despite the large number of studies reporting the length-weight relationship for lionfish.

Here, we compare previously published length-weight relationships for lionfish populations in North Carolina, Northern and Southern Gulf of Mexico, the Southern Mexican Caribbean, Bahamas, Little Cayman, Jamaica, Bonaire, Puerto Rico, and Costa Rica \citep{barbour_2011,fogg_2013,dahl_2014,aguilarperera_2016,sabidoitza_2016,sabidoitz_2016,darling_2011,edwards_2014,chin_2016,deleon_2013,toledohernndez_2014,sandel_2015}. We also collected lionfish length and weight data in the central Mexican Caribbean and report the first allometric growth equation for this region. The objective of this paper is to describe the spatial pattern of length-weight relationships of lionfish across the Caribbean and Western Atlantic and to discuss implications of these spatial differences.

@@

We reviewed 12 published studies and obtained 17 length-weight relationships for the North Atlantic (n = 1), Gulf of Mexico (n = 7), and Caribbean (n = 9, Table \ref{tab:all_params}, Fig \ref{fig:all_allo}). We collected information on sampling methods, sex differentiation, location, and depth ranges from each study when available. Only two studies reported parameters for each gender \citep{aguilarperera_2016,fogg_2013}, so we assumed both genders were included in a study if gender was unspecified. Reviewed studies presented information for organisms obtained at depths between `r min(review$minD, na.rm = T)` m and `r max(review$maxD, na.rm = T)` m. Three studies explicitly stated that their organisms were sampled with pole spears \citep{aguilarperera_2016,chin_2016,dahl_2014,sabidoitz_2016}, and five studies mentioned that some of their organisms were obtained with pole spears (or other type of harpoon) but also hand-held nets or fish traps \citep{sandel_2015,barbour_2011,fogg_2013,edwards_2014,sabidoitza_2016,sabidoitz_2016,toledohernndez_2014}, and two studies did not specify how organisms were sampled \citep{deleon_2013,darling_2011}. \citet{fogg_2013} use spineless weight in their calculations, so their parameters likely underestimated total wieght. Since no spineless to total weight conversions were available, these parameters were taken as reported.

@@

Where $a$ is the ponderal index and $b$ is the scaling exponent or allometric parameter. Transforming this equation via base-10 logarithms:

@@

Where $Y = log_{10}(TW)$, $X = log_{10}(TL)$, and $c = log_{10}(a)$. The coefficients ($c$ and $b$) were estimated with  an Ordinary Least Squares Regression and heteroskedastic-robust standard error correction \citep{zeileis_2004}. When the $b = 3$, it is said that the organism exhibits a perfect isometric growth, so the $b$ coefficient was tested against the null hypothesis of isometric growth (*i.e.* $H_0: b = 3$). Coefficients were tested with a two-tailed Student's t, and the significance of the regression was corroborated with an F-test.

@@

We obtained a total of 18 parameter pairs by combining length-weight parameters extracted from the literature and the additional pair calculated here. We used the central Mexican Caribbean as a case study of how the use of *ex situ* parameters influences the accuracy of weight estimates for lionfish. We estimated TW from the TL observations we collected in the central Mexican Caribbean (n = 109) using each of the 18 parameter pairs and divided predicted weights by known observed weights to obtain a simple measure of over- or underestimation. Difference in mean weight ratios across the different parameter pairs were tested with a one-way analysis of variance (ANOVA) and Tukey's test was used for post-hoc tests. All analyses were performed in R version `r paste(version$major, version$minor, sep = ".")` \citep{rcore_2018}. Raw data and code used in this work are available at dryad.org.

@@

Figure \ref{fig:all_allo} shows all 18 weight-at-length relationships. Parameters from models fit to males or females exclusively tend to have a higher steepness (*i.e.* higher allometric parameter), with mean $\pm$ standard deviation values of $b = `r formatC(mean(review$b[review$Gender == "Male"]), digits = 2, format = "f")` \pm `r formatC(sd(review$b[review$Gender == "Male"]), digits = 2, format = "f")`$ and $b = `r formatC(mean(review$b[review$Gender == "Female"]), digits = 2, format = "f")` \pm `r formatC(sd(review$b[review$Gender == "Female"]), digits = 2, format = "f")`$ for males and females respectively, compared to parameters from models for combined genders with a mean $\pm$ standard deviation value of $b = `r formatC(mean(review$b[review$Gender == "Both"]), digits = 2, format = "f")` \pm `r formatC(sd(review$b[review$Gender == "Both"]), digits = 2, format = "f")`$. In the case of the ponderal index ($a$) and its $log_{10}$ transformation ($c$), values were higher for parameters for combined genders.

<!-- In the above paragraph, I don't understand why we care whether individual gender coefficients are different than the pooled genders.  You need to explain why that matters somewhere in the discussion or something.  Could pooling samples together be a mistake?  If there are substantially more males or females in a given study, could that skew the results? How much?  Enough to make the equation unreliable? Or are these gender differences fairly minor?  I don't think you can just say "pooling genders leads to lower steepness" and then gloss over it/ ignore ift for the rest of the paper -->

There were significant differences in our predicted weights for the central Mexican Caribbean when using the different pairs of parameters ($F(df = 15; 1728) = 38.26; p < 0.001$). Weight estimates using parameters from the Gulf of Mexico and North-Western Atlantic were higher on average than those from the Caribbean. The average ($\pm$ SD) predicted-to-observed weight ratios from these three regions were 1.24 $\pm$ 0.309, 1.76 $\pm$ 0.496, and 1.17 $\pm$ 0.398, respectively. The lowest weight estimates resulted from using the allometric parameters from Banco Chinchorro in the Caribbean \citet{sabidoitz_2016}, and the highest weight estimates came from the Northern Atlantic \citep{barbour_2011}. The calculated ratio of predicted-to-observed weight  ranged from `r filter(Predicted_biomass, Study_id == "Sabido2BC") %$% mean(Biomass_ratio) %>% formatC(digits = 2, format = "f")` $\pm$ `r filter(Predicted_biomass, Study_id == "Sabido2BC") %$% sd(Biomass_ratio) %>% formatC(digits = 2, format = "f")` to `r filter(Predicted_biomass, Study_id == "Barbour") %$% mean(Biomass_ratio) %>% formatC(digits = 2, format = "f")` $\pm$ `r filter(Predicted_biomass, Study_id == "Barbour") %$% sd(Biomass_ratio) %>% formatC(digits = 2, format = "f")` (mean $\pm$ SD). Tukey's post-hoc test suggests that weight ratios for the central Mexican Caribbean were not different from those obtained with parameters from Little Cayman, the Bahamas, and some sites in the Gulf of Mexico (Tukeys HSD $p > 0.05$). Predicted-to-observed weight ratios are presented in Figure \ref{fig:bio_ratio}. Spineless weight parameters from \citet{fogg_2013} still produced predicted-to-observed weight ratios > 1.

<!-- Include the actual mean values (+/- SD) in the sentence "The lowest weight estimates resulted from using the allometric parameters from Banco Chinchorro in the Caribbean \citet{sabidoitz_2016}, and the highest weight estimates came from the Northern Atlantic \citep{barbour_2011}" -->

@@

We  detected substantial differences in weight-at-length between organisms from the Caribbean, Gulf of Mexico, and North-Western Atlantic. Groupings of predicted-to-observed weight ratios aligned with the spatial distribution of the examined studies, suggesting that these differences are mediated by space. These regional allometric differences mirror similar patterns in age-at-length of lionfish across both their invaded and native regions \citep{pusack_2016}. Variation may be driven by genetics or by organisms' exposure to distinct environmental conditions. For example, \citet{betancurr_2011} used mitochondrial DNA to demonstrate the existence of two distinct population groups, identified as the “Caribbean group” and “Northern Group”, and \citet{fogg_2015} alternatively suggested that age-at-length differences may be climate-driven. Differences in weight-at-length could also reflect differential energy input or usage, or a combination of both. Future research is needed to determine which processes are at work here.

Differences in length-weight relationships have traditionally been highlighted as potential pitfalls to fishery management. For example, \citet{wilson_2012} show that small-scale variations in length-at-age and fishing mortality in other Scorpaeniformes translate to differential landings, effort, and catch per unit effort in the live fish fishery of California, and that these differences must be taken into account in management plans. The lionfish case poses the opposite scenario, where the manager desires to eradicate species. To accurately gauge both the effectiveness of lionfish removal efforts and the resources needed to successfully manage an invasion, we must acknowledge and understand regional biological differences in important variables such as allometric growth parameters.

The results presented here have major implications for management. For example, \citet{edwards_2014} simulated a lionfish culling program under two scenarios, one using length-at-age and length-to-weight parameters from North Carolina and one using parameters from Little Cayman. Their results show that using different parameters caused up to a four-year difference in the time required for the simulated lionfish population to recover to 90% of its initial biomass after removals ceased. Here, we show that using one set of length-weight parameters versus another for a given length can result in up to a threefold overestimation of TW. These spatially-driven differences become especially important when allocating resources for lionfish removal programs, incentivizing lionfish fisheries as a source of alternative livelihoods, or estimating ecosystem impacts. Research efforts focused on invasive lionfish populations need to use parameters calculated for their region to the extent possible, or at least use reasonable sets of different parameters that provide upper and lower bounds in their results.

\section*{Acknowledgements}
